Maps

### 2020-04-27 ms_8.Rmd
Final commit of ms_8 draft (sans original datafiles)

# See implement plot (plot2) saved as gif

@@

@@

@@

saveRDS(Census_1870, file = "final/1870.rds")
saveRDS(Census_1880, file = "final/1880.rds")
saveRDS(Census_1890, file = "final/1890.rds")
saveRDS(Census_1900, file = "final/1900.rds")
saveRDS(Census_1910, file = "final/1910.rds")
saveRDS(Census_1920, file = "final/1920.rds")
saveRDS(Census_1930, file = "final/1930.rds")
saveRDS(Census_1940, file = "final/1940.rds")
saveRDS(Census_1950, file = "final/1950.rds")
saveRDS(Census_1960, file = "final/1960.rds")

>>>>

# See implement plot (plot2) saved as gif
# also use cowedu model

@@

cows_size_model <- allData %>%
  select(YEAR, pct_enrolled, cows_per_farm, avg_size) %>%
  na.omit() %>%
  lm(pct_enrolled ~ cows_per_farm*avg_size, data = .) %>%
  tidy(conf.int = TRUE)

saveRDS(cows_size_model, "final/cows_size_model.rds")

@@

saveRDS(cowedu_model, "final/cowedu_model.rds")

@@
